Modelling the City of Melbourne Pedestrian Data

### 2017-10-01 presentation/final.Rmd
added slide for questions

---
## Acknowledgements
- R and RStudio
- Packages used for this work were: 
  * `dplyr`, `lubridate` and `tidyr` for data manipulation
  * `foreach` and `doSNOW` for parallel computing
  * `rwalkr` for accessing latest data (Thanks Earo!)
  * `ggplot2` and `ggmap` for visualisations
  * `xaringan` for compliling this presentation
- Code, presentation and thesis at [github.com:gavinchin/honours2017](github.com:gavinchin/honours2017)

>>>>

---
## Acknowledgements
- R and RStudio
- Packages used for this work were: 
  * `dplyr`, `lubridate` and `tidyr` for data manipulation
  * `foreach` and `doSNOW` for parallel computing
  * `rwalkr` for accessing latest data (Thanks Earo!)
  * `ggplot2` and `ggmap` for visualisations
  * `xaringan` for compliling this presentation
- Code, presentation and thesis at [github.com/gavinchin/honours2017](https://github.com/gavinchin/honours2017)

I'd like to thank Di Cook and Earo Wang for helping me with the project, as well as my fellow honours classmates.

---
class: inverse, center
# Questions or comments?

--

## Thanks for listening!
